---
title: "Resiliency Food Model"
author: "S. Kelly"
date: "2024-06-20"
output: html_document
---


```{r, include = F}
library(tidyverse)
library(car) #for vif analysis
options(scipen = 999)
```

```{r, results = 'hide'}
# Importing the revised dataset with the 2018 IL data for child_elig
Final_Variables_June_2024 <-
read.csv("~/Desktop/R Directory/resiliency_collab/data/Final_Variables_June_2024.csv")

glimpse(Final_Variables_June_2024)
```

# Food Model
## DV 1: FI Percent

```{r}
# Histogram using the z-scored FI Percent
hist(Final_Variables_June_2024$z_fi_percent)
```

```{r}
#just checking the RAW variables (unique only) for FI Percent
unique(round(Final_Variables_June_2024$fi_percent)) #note:rounded to whole for quicker checks
summary(Final_Variables_June_2024$fi_percent)
```

```{r}
# 206 missing values #Where are the NAs?
missing_fi_percent <-
Final_Variables_June_2024 %>% 
filter(is.na(fi_percent)) # Missing values are Illinois and Kansas
table(missing_fi_percent$State.x) # IL (101) and KS (105)
```

## DV 2: Child Elig Lunch Perc
### Note: Using New Variable (new_childelig), which incorporated the 2018 IL data
```{r}
# Histogram using the z-scored z_new_childelig
hist(Final_Variables_June_2024$z_new_childelig)
```

```{r}
#just checking the RAW variables (unique only) for new_childelig
unique(round(Final_Variables_June_2024$new_childelig)) # note: rounded to whole for quicker checks
summary(Final_Variables_June_2024$new_childelig) # 227 missing values
```

```{r}
# Where are the NAs? Primarily Kansas and Tennessee
missing_child <- Final_Variables_June_2024 %>% 
  filter(is.na(new_childelig)) 

table(missing_child$State.x)
```

```{r}
# Did we resolve the strange IL values? Yes.  
strange_values_child <-
Final_Variables_June_2024 %>% 
filter(new_childelig < abs(5))
table(strange_values_child$State.x)
```

# Building the Models

# DV 1: FI Percent

## IV: Demographics (9 variables), DV: FI Percent

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_fi_just_demos <- lm(formula = z_fi_percent ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE, data = Final_Variables_June_2024) 
summary(z_fi_just_demos)
```

## Confidence Intervals for Demographic IVs

```{r}
confint(z_fi_just_demos)
```

## VIF for Demographic IVs

```{r}
vif(z_fi_just_demos)
```

## IV: Food & Housing (12 variables), DV: FI Percent
### Note: FI Percent and Child Lunch Elig Removed from IVs

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=50)}
z_fi_just_foodhouse <- lm(formula = z_fi_percent ~ z_food_afford + z_fd_enviro_indx + z_ACS_PCT_FOOD_STAMP + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE, data = Final_Variables_June_2024)
summary(z_fi_just_foodhouse)
```
## Confidence Intervals for Food & Housing IVs

```{r}
confint(z_fi_just_foodhouse)
```

## VIF for Food & Housing IVs

```{r}
vif(z_fi_just_foodhouse)
```

## IV: Education (3 variables), DV: FI Percent

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_fi_just_ed <- lm(formula = z_fi_percent ~ z_hsg_rate + z_sc_percent + z_ms_average, data = Final_Variables_June_2024)
summary(z_fi_just_ed)
```

## Confidence Intervals for Education IVs

```{r}
confint(z_fi_just_ed)
```

## VIF for Education IVs

```{r}
vif(z_fi_just_ed)
```

## IV: Technology (3 variables), DV: FI Percent

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_fi_just_tech <- lm(formula = z_fi_percent ~ z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_ACS_PCT_BROADBAND, data = Final_Variables_June_2024)
summary(z_fi_just_tech)
```
## Confidence Intervals for Technology IVs

```{r}
confint(z_fi_just_tech)
```

## VIF for Technology IVs

```{r}
vif(z_fi_just_tech)
```

## IV: HWCC (7 variables), DV: FI Percent

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_fi_just_HWCC <- lm(formula = z_fi_percent ~ z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB, data = Final_Variables_June_2024)
summary(z_fi_just_HWCC)
```

## Confidence Intervals for HWCC IVs

```{r}
confint(z_fi_just_HWCC)
```

## VIF for HWCC IVs

```{r}
vif(z_fi_just_HWCC)
```

## IV: Health A (6 variables), DV: FI Percent

```{r, tidy=TRUE, tidy.opts= list(width.cutoff = 60)}
z_fi_just_healthA <- lm(formula = z_fi_percent ~ z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_opcp_rate + z_TeenBirths, data = Final_Variables_June_2024)
summary(z_fi_just_healthA)
```

## Confidence Intervals for Health A IVs

```{r}
confint(z_fi_just_healthA)
```

## VIF for Health A IVs

```{r}
vif(z_fi_just_healthA)
```

## IV: Health B (5 variables), DV: FI Percent

```{r, tidy=TRUE, tidy.opts= list(width.cutoff = 60)}
z_fi_just_healthB <- lm(formula = z_fi_percent ~ z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC, data = Final_Variables_June_2024)
summary(z_fi_just_healthB)
```

## Confidence Intervals for Health B IVs

```{r}
confint(z_fi_just_healthB)
```

## VIF for Health B IVs

```{r}
vif(z_fi_just_healthB)
```

## IV: Business (4 variables), DV: FI Percent

```{r, tidy=TRUE, tidy.opts= list(width.cutoff = 60)}
z_fi_just_bus <- lm(formula = z_fi_percent ~ z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_ACS_GINI_INDEX + z_unemp_perc, data = Final_Variables_June_2024)
summary(z_fi_just_bus)
```

## Confidence Intervals for Business IVs

```{r}
confint(z_fi_just_bus)
```

## VIF for Business IVs

```{r}
vif(z_fi_just_bus)
```

## IV: Government (5 variables), DV: FI Percent

```{r, tidy=TRUE, tidy.opts= list(width.cutoff = 60)}
z_fi_just_gov <- lm(formula = z_fi_percent ~ z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Final_Variables_June_2024)
summary(z_fi_just_gov)
```

## Confidence Intervals for Government IVs

```{r}
confint(z_fi_just_gov)
```

## VIF for Government IVs

```{r}
vif(z_fi_just_gov)
```

# Final Food Model, DV: FI Percent; IVs: 54

```{r, tidy=TRUE, tidy.opts=list(width.cutoff = 60)}
z_fi_levels_12345678 <- lm(formula = z_fi_percent ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_food_afford + z_fd_enviro_indx + z_ACS_PCT_FOOD_STAMP + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE + z_hsg_rate + z_sc_percent + z_ms_average + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_ACS_PCT_BROADBAND + z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_opcp_rate + z_TeenBirths + z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_ACS_GINI_INDEX + z_unemp_perc + z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Final_Variables_June_2024)
summary(z_fi_levels_12345678)
```

## Confidence Intervals for Final Model

```{r}
confint(z_fi_levels_12345678)
```

## VIF for Final Model

```{r}
vif(z_fi_levels_12345678)
```

# DV 2: Child Elig Lunch Perc
### Note: Using New Variable (z_new_childelig), which incorporated the 2018 IL data

## IV: Demographics (9 variables), DV: Child Elig Lunch Perc

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_ce_just_demos <- lm(formula = z_new_childelig ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE, data = Final_Variables_June_2024) 
summary(z_ce_just_demos)
```

## Confidence Intervals for Demographic IVs

```{r}
confint(z_ce_just_demos)
```

## VIF for Demographic IVs

```{r}
vif(z_ce_just_demos)
```

## IV: Food & Housing (12 variables), DV: Child Elig Lunch Perc
### Note: FI Percent and Child Lunch Elig Removed from IVs

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=50)}
z_ce_just_foodhouse <- lm(formula = z_new_childelig ~ z_food_afford + z_fd_enviro_indx + z_ACS_PCT_FOOD_STAMP + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE, data = Final_Variables_June_2024)
summary(z_ce_just_foodhouse)
```
## Confidence Intervals for Food & Housing IVs

```{r}
confint(z_ce_just_foodhouse)
```

## VIF for Food & Housing IVs

```{r}
vif(z_ce_just_foodhouse)
```

## IV: Education (3 variables), DV: Child Elig Lunch Perc

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_ce_just_ed <- lm(formula = z_new_childelig ~ z_hsg_rate + z_sc_percent + z_ms_average, data = Final_Variables_June_2024)
summary(z_ce_just_ed)
```

## Confidence Intervals for Education IVs

```{r}
confint(z_ce_just_ed)
```

## VIF for Education IVs

```{r}
vif(z_ce_just_ed)
```

## IV: Technology (3 variables), DV: Child Elig Lunch Perc

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_ce_just_tech <- lm(formula = z_new_childelig ~ z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_ACS_PCT_BROADBAND, data = Final_Variables_June_2024)
summary(z_ce_just_tech)
```
## Confidence Intervals for Technology IVs

```{r}
confint(z_ce_just_tech)
```

## VIF for Technology IVs

```{r}
vif(z_ce_just_tech)
```

## IV: HWCC (7 variables), DV: Child Elig Lunch Perc

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_ce_just_HWCC <- lm(formula = z_new_childelig ~ z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB, data = Final_Variables_June_2024)
summary(z_ce_just_HWCC)
```

## Confidence Intervals for HWCC IVs

```{r}
confint(z_ce_just_HWCC)
```

## VIF for HWCC IVs

```{r}
vif(z_ce_just_HWCC)
```

## IV: Health A (6 variables), DV: Child Elig Lunch Perc

```{r, tidy=TRUE, tidy.opts= list(width.cutoff = 60)}
z_ce_just_healthA <- lm(formula = z_new_childelig ~ z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_opcp_rate + z_TeenBirths, data = Final_Variables_June_2024)
summary(z_ce_just_healthA)
```

## Confidence Intervals for Health A IVs

```{r}
confint(z_ce_just_healthA)
```

## VIF for Health A IVs

```{r}
vif(z_ce_just_healthA)
```

## IV: Health B (5 variables), DV: Child Elig Lunch Perc

```{r, tidy=TRUE, tidy.opts= list(width.cutoff = 60)}
z_ce_just_healthB <- lm(formula = z_new_childelig ~ z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC, data = Final_Variables_June_2024)
summary(z_ce_just_healthB)
```

## Confidence Intervals for Health B IVs

```{r}
confint(z_ce_just_healthB)
```

## VIF for Health B IVs

```{r}
vif(z_ce_just_healthB)
```

## IV: Business (4 variables), DV: Child Elig Lunch Perc

```{r, tidy=TRUE, tidy.opts= list(width.cutoff = 60)}
z_ce_just_bus <- lm(formula = z_new_childelig ~ z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_ACS_GINI_INDEX + z_unemp_perc, data = Final_Variables_June_2024)
summary(z_ce_just_bus)
```

## Confidence Intervals for Business IVs

```{r}
confint(z_ce_just_bus)
```

## VIF for Business IVs

```{r}
vif(z_ce_just_bus)
```

## IV: Government (5 variables), DV: Child Elig Lunch Perc

```{r, tidy=TRUE, tidy.opts= list(width.cutoff = 60)}
z_ce_just_gov <- lm(formula = z_new_childelig ~ z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Final_Variables_June_2024)
summary(z_ce_just_gov)
```

## Confidence Intervals for Government IVs

```{r}
confint(z_ce_just_gov)
```

## VIF for Government IVs

```{r}
vif(z_ce_just_gov)
```

# Final Food Model, DV: Child Elig Lunch Perc; IVs: 54

```{r, tidy=TRUE, tidy.opts=list(width.cutoff = 60)}
z_ce_levels_12345678 <- lm(formula = z_new_childelig ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_food_afford + z_fd_enviro_indx + z_ACS_PCT_FOOD_STAMP + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE + z_hsg_rate + z_sc_percent + z_ms_average + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_ACS_PCT_BROADBAND + z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_opcp_rate + z_TeenBirths + z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_ACS_GINI_INDEX + z_unemp_perc + z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Final_Variables_June_2024)
summary(z_ce_levels_12345678)
```

## Confidence Intervals for Final Model

```{r}
confint(z_ce_levels_12345678)
```

## VIF for Final Model

```{r}
vif(z_ce_levels_12345678)
```