---
title: "Government Model"
author: "S.Kelly"
format: pdf
editor: visual
execute: 
  warning: FALSE
---

```{r loading the packages, include=FALSE}
library(tidyverse)
library(readxl)
library(car) #for vif analysis
```

```{r loading the data, include = FALSE}
Z_and_Final_Variables_10.28.22 <- read.csv("~/Desktop/R Directory/ResiliencyProject/Z_and_Final_Variables_10.28.22.csv")
```

## Updated 11-9-23; Change made: removed *z_uc_percent* as an IV

## DV Histogram (Access to Exercise Opportunities)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
ggplot(data = Z_and_Final_Variables_10.28.22, mapping = aes(x = z_aeo_perc_w_acc)) + geom_histogram() + labs(y = NULL)
```

```{r}
options(scipen = 990) #turning off scientific notation for coefficients
```

# Government Model Groupings

## Outcome: Access to Exercise Opportunities

## IVs: Demographics Only (9 variables)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_aeo_just_demos <- lm(formula = z_aeo_perc_w_acc ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE, data = Z_and_Final_Variables_10.28.22) 
summary(z_aeo_just_demos)
```

## Confidence Intervals for Demographic IVs

```{r}
confint(z_aeo_just_demos)
```

## VIF for Demographic IVs

```{r}
vif(z_aeo_just_demos)
```

## Outcome: Access to Exercise Opportunities

## IVs: Food & Housing Only (14 variables)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_aeo_just_foodhouse <- lm(formula = z_aeo_perc_w_acc ~ z_food_afford + z_fd_enviro_indx + z_fi_percent + z_ACS_PCT_FOOD_STAMP + z_childelig_lunch_perc + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE, data = Z_and_Final_Variables_10.28.22)
summary(z_aeo_just_foodhouse)
```

## Confidence Intervals for Food & Housing IVs

```{r}
confint(z_aeo_just_foodhouse)
```

## VIF for Food & Housing IVs

```{r}
vif(z_aeo_just_foodhouse)
```

## Outcome: Access to Exercise Opportunities

## IVs: Education (3 variables)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_aeo_just_ed <- lm(formula = z_aeo_perc_w_acc ~ z_hsg_rate + z_sc_percent + z_ms_average, data = Z_and_Final_Variables_10.28.22)
summary(z_aeo_just_ed)
```

## Confidence Intervals for Education IVs

```{r}
confint(z_aeo_just_ed)
```

## VIF for Education IVs

```{r}
vif(z_aeo_just_ed)
```

## Outcome: Access to Exercise Opportunities

## IVs: Technology (3 variables)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_aeo_just_tech <- lm(formula = z_aeo_perc_w_acc ~ z_ACS_PCT_BROADBAND + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE, data = Z_and_Final_Variables_10.28.22)
summary(z_aeo_just_tech)
```

## Confidence Intervals for Technology IVs

```{r}
confint(z_aeo_just_tech)
```

## VIF for Technology IVs

```{r}
vif(z_aeo_just_tech)
```

## Outcome: Access to Exercise Opportunities

## IVs: HWCC (7 variables)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_aeo_just_HWCC <- lm(formula = z_aeo_perc_w_acc ~ z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB, data = Z_and_Final_Variables_10.28.22)
summary(z_aeo_just_HWCC)
```

## Confidence Intervals for HWCC IVs

```{r}
confint(z_aeo_just_HWCC)
```

## VIF for HWCC IVs

```{r}
vif(z_aeo_just_HWCC)
```

## Outcome: Access to Exercise Opportunities

## IVs: Health A (7 variables)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_aeo_just_healthA <- lm(formula = z_aeo_perc_w_acc ~ z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_opcp_rate + z_TeenBirths, data = Z_and_Final_Variables_10.28.22)
summary(z_aeo_just_healthA)
```

## Confidence Intervals for Health A IVs

```{r}
confint(z_aeo_just_healthA)
```

## VIF for Health A IVs

```{r}
vif(z_aeo_just_healthA)
```

## Outcome: Access to Exercise Opportunities

## IVs: Health B (5 variables)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_aeo_just_healthB <- lm(formula = z_aeo_perc_w_acc ~ z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC, data = Z_and_Final_Variables_10.28.22)
summary(z_aeo_just_healthB)
```

## Confidence Intervals for Health B IVs

```{r}
confint(z_aeo_just_healthB)
```

## VIF for Health B IVs

```{r}
vif(z_aeo_just_healthB)
```

## Outcome: Access to Exercise Opportunities

## IVs: Business (4 variables)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_aeo_just_bus <- lm(formula = z_aeo_perc_w_acc ~ z_unemp_perc + z_ACS_GINI_INDEX + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR, data = Z_and_Final_Variables_10.28.22)
summary(z_aeo_just_bus)
```

## Confidence Intervals for Business IVs

```{r}
confint(z_aeo_just_bus)
```

## VIF for Business IVs

```{r}
vif(z_aeo_just_bus)
```

## Outcome: Access to Exercise Opportunities

## IVs: Government (4 variables; removed AEO)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_aeo_just_gov <- lm(formula = z_aeo_perc_w_acc ~ z_soc_assoc_num + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Z_and_Final_Variables_10.28.22)
summary(z_aeo_just_gov)
```

## Confidence Intervals for Government IVs

```{r}
confint(z_aeo_just_gov)
```

## VIF for Government IVs

```{r}
vif(z_aeo_just_gov)
```

## Full Government Model

## Outcome: Access to Exercise Opportunities

## IVs: 56

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_aeo_levels_12345678 <- lm(formula = z_aeo_perc_w_acc ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_food_afford + z_fd_enviro_indx + z_fi_percent + z_ACS_PCT_FOOD_STAMP + z_childelig_lunch_perc + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE + z_hsg_rate + z_sc_percent + z_ms_average + z_ACS_PCT_BROADBAND + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_opcp_rate + z_TeenBirths + z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC + z_unemp_perc + z_ACS_GINI_INDEX + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_soc_assoc_num + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Z_and_Final_Variables_10.28.22)
summary(z_aeo_levels_12345678)
```

## Confidence Intervals for Full Government Model IVs

```{r}
confint(z_aeo_levels_12345678)
```

## VIF for Full Government Model IVs

```{r}
vif(z_aeo_levels_12345678)
```
