---
title: "Resiliency Collab"
author: "S.Kelly"
format: pdf
editor: visual
---

# Final Models: Education (hsg & sc), Health (lbw, pud, mud), and Housing (rent30, median, owned)

### To address VIF, dropped the following three IVs from all previous final models: z_SVI_RPL_THEMES_ALL, z_ACS_PER_CAPITA_INCOME, z_pfh_percent

```{r loading the packages, include=FALSE}
library(tidyverse)
library(readxl)
library(car) #for vif analysis
```

```{r loading the data, include = FALSE}
Z_and_Final_Variables_10.28.22 <- read.csv("~/Desktop/R Directory/ResiliencyProject/Z_and_Final_Variables_10.28.22.csv")
```

```{r}
dim(Z_and_Final_Variables_10.28.22)
glimpse(Z_and_Final_Variables_10.28.22)
```

# Final Education Model
## DV: High School Rate
## IVs: Demographics, Food/Housing, Technology, Health 1, (DOES NOT INCLUDE health 2), HWCC, Business, Government

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
options(scipen = 999)
z_hsg_levels_1234678 <- lm(formula = z_hsg_rate ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_food_afford + z_fd_enviro_indx + z_fi_percent + z_ACS_PCT_FOOD_STAMP + z_childelig_lunch_perc + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE + z_ACS_PCT_BROADBAND + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_uc_percent + z_opcp_rate + z_TeenBirths + z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_unemp_perc + z_ACS_GINI_INDEX + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Z_and_Final_Variables_10.28.22) 
summary(z_hsg_levels_1234678)
```

## Final Education Model, High School Rate
## Confidence Intervals

```{r}
confint(z_hsg_levels_1234678)
```

## Final Education Model, High School Rate
## VIF

```{r}
vif(z_hsg_levels_1234678)
```

# Final Education Model
## DV: Some College
## IVs: Demographics, Food/Housing, Technology, Health 1, Health 2, HWCC, Business, Government

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_sc_levels_12345678 <- lm(formula = z_sc_percent ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_food_afford + z_fd_enviro_indx + z_fi_percent + z_ACS_PCT_FOOD_STAMP + z_childelig_lunch_perc + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE + z_ACS_PCT_BROADBAND + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_uc_percent + z_opcp_rate + z_TeenBirths + z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC + z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_unemp_perc + z_ACS_GINI_INDEX + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Z_and_Final_Variables_10.28.22) 
summary(z_sc_levels_12345678)
```

## Final Education Model, Some College
## Confidence Intervals

```{r}
confint(z_sc_levels_12345678)
```

## Final Education Model, Some College
## VIF

```{r}
vif(z_sc_levels_12345678)
```

# Final Health Model
## DV: Low Birth Weight
## IVs: Demographics, Health 1, Health 2, Food/Housing, Technology, HWCC, Business, Government

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_lbw_levels_12345678 <- lm(formula = z_lbw_percent_lbw ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_uc_percent + z_opcp_rate + z_TeenBirths + z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC + z_food_afford + z_fd_enviro_indx + z_fi_percent + z_ACS_PCT_FOOD_STAMP + z_childelig_lunch_perc + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE + z_ACS_PCT_BROADBAND + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_unemp_perc + z_ACS_GINI_INDEX + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Z_and_Final_Variables_10.28.22) 
summary(z_lbw_levels_12345678)
```

## Final Health Model, Low Birth Weight
## Confidence Intervals

```{r}
confint(z_lbw_levels_12345678)
```

# Final Health Model, Low Birth Weight
## VIF

```{r}
vif(z_lbw_levels_12345678)
```

# Final Health Model
## DV: Physically Unhealthy Days
## IVs: Demographics, Health 1, Health 2, Food/Housing, Technology, HWCC, Business, Government
### Note: z_pfh_percent was previously excluded from the final physically unhealthy days model

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_pphd_levels_12345678 <- lm(formula = z_pphd_avgnum ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_uc_percent + z_opcp_rate + z_TeenBirths + z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC + z_food_afford + z_fd_enviro_indx + z_fi_percent + z_ACS_PCT_FOOD_STAMP + z_childelig_lunch_perc + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE + z_ACS_PCT_BROADBAND + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_unemp_perc + z_ACS_GINI_INDEX + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Z_and_Final_Variables_10.28.22) 
summary(z_pphd_levels_12345678)
```

## Final Health Model, Physically Unhealthy Days
## Confidence Intervals

```{r}
confint(z_pphd_levels_12345678)
```

## Final Health Model, Physically Unhealthy Days
## VIF

```{r}
vif(z_pphd_levels_12345678)
```

# Final Health Model
## DV: Mentally Unhealthy Days
## IVs: Demographics, Health 1, Health 2, Food/Housing, Technology, HWCC, Business, Government
### Note: z_pfh_percent was previously excluded from the final mentally unhealthy days model

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_pmhd_levels_12345678 <- lm(formula = z_pmhd_avgnum ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_uc_percent + z_opcp_rate + z_TeenBirths + z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC + z_food_afford + z_fd_enviro_indx + z_fi_percent + z_ACS_PCT_FOOD_STAMP + z_childelig_lunch_perc + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_RENT_COST_30PCT + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNED_HH + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_MEDIAN_HOME_VALUE + z_ACS_PCT_BROADBAND + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_unemp_perc + z_ACS_GINI_INDEX + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Z_and_Final_Variables_10.28.22) 
summary(z_pmhd_levels_12345678)
```

## Final Health Model, Mentally Unhealthy Days
## Confidence Intervals

```{r}
confint(z_pmhd_levels_12345678)
```

## Final Health Model, Mentally Unhealthy Days
## VIF

```{r}
vif(z_pmhd_levels_12345678)
```

# Final Housing Model
## DV: Rent 30 Percent
## IVs: Excludes those IVs that serve as DVs in the housing models -- z_ACS_PCT_RENT_COST_30PCT, z_ACS_MEDIAN_HOME_VALUE, z_ACS_PCT_OWNED_HH -- and the three problematic VIF IVs
### Note: Building final model below (R markdown housing doc had groupings only)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_rent30_levels_12345678 <-lm(formula = z_ACS_PCT_RENT_COST_30PCT ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_food_afford + z_fd_enviro_indx + z_fi_percent + z_ACS_PCT_FOOD_STAMP + z_childelig_lunch_perc + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_PCT_BROADBAND + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_uc_percent + z_opcp_rate + z_TeenBirths + z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC + z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_unemp_perc + z_ACS_GINI_INDEX + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Z_and_Final_Variables_10.28.22) 
summary(z_rent30_levels_12345678)
```

## Final Housing Model, Rent 30 Percent
## Confidence Intervals

```{r}
confint(z_rent30_levels_12345678)
```

## Final Housing Model, Rent 30 Percent
## VIF

```{r}
vif(z_rent30_levels_12345678)
```

# Final Housing Model
## DV: Median Home Value
## IVs: Excludes those IVs that serve as DVs in the housing models -- z_ACS_PCT_RENT_COST_30PCT, z_ACS_MEDIAN_HOME_VALUE, z_ACS_PCT_OWNED_HH -- and the three problematic VIF IVs
### Note: Building final model below (R markdown housing doc had groupings only)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_median_levels_12345678 <-lm(formula = z_ACS_MEDIAN_HOME_VALUE ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_food_afford + z_fd_enviro_indx + z_fi_percent + z_ACS_PCT_FOOD_STAMP + z_childelig_lunch_perc + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_PCT_BROADBAND + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_uc_percent + z_opcp_rate + z_TeenBirths + z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC + z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_unemp_perc + z_ACS_GINI_INDEX + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Z_and_Final_Variables_10.28.22) 
summary(z_median_levels_12345678)
```

## Final Housing Model, Median Home Value
## Confidence Intervals

```{r}
confint(z_median_levels_12345678)
```

## Final Housing Model, Median Home Value
## VIF

```{r}
vif(z_median_levels_12345678)
```

# Final Housing Model
## DV: Owned HH
## IVs: Excludes those IVs that serve as DVs in the housing models -- z_ACS_PCT_RENT_COST_30PCT, z_ACS_MEDIAN_HOME_VALUE, z_ACS_PCT_OWNED_HH -- and the three problematic VIF IVs
### Note: Building final model below (R markdown housing doc had groupings only)

```{r, tidy = TRUE, tidy.opts = list(width.cutoff=60)}
z_owned_levels_12345678 <-lm(formula = z_ACS_PCT_OWNED_HH ~ z_ACS_PCT_BLACK + z_ACS_PCT_HISPAN + z_SVI_RPL_THEME1_SOCIECO + z_SVI_RPL_THEME2_HH_DISB + z_SVI_RPL_THEME3_MINO + z_SVI_RPL_THEME4_HH_TRANS + z_ACS_PCT_ENGL_NOT_WELL + z_ACS_PCT_NON_CITIZEN + z_ACS_MEDIAN_AGE + z_food_afford + z_fd_enviro_indx + z_fi_percent + z_ACS_PCT_FOOD_STAMP + z_childelig_lunch_perc + z_shp_percent + z_shcb_percent + z_ACS_PCT_NO_VEH + z_ACS_PCT_RENTER_HH_CHILD + z_ACS_PCT_MOBILE_HOME + z_ACS_PCT_OWNER_HH_CHILD + z_ACS_PCT_BROADBAND + z_ACS_PCT_NO_PC + z_ACS_PCT_SMARTPHONE + z_phys_per_cap + z_mhp_per_cap + z_dents_per_cap + z_uninsur_perc + z_uc_percent + z_opcp_rate + z_TeenBirths + z_phs_rate + z_ms_perc_ann + z_AMFAR_AMATFAC + z_MP_PERCPEN + z_AHRF_RURAL_H_CLINIC + z_pphd_avgnum + z_pmhd_avgnum + z_lbw_percent_lbw + z_pi_phy_inact + z_cip_perc + z_csph_perc + z_ACS_PCT_CHILD_DISAB + z_unemp_perc + z_ACS_GINI_INDEX + z_ACS_MEDIAN_HH_INCOME + z_ACS_PCT_WORK_NO_CAR + z_soc_assoc_num + z_aeo_perc_w_acc + z_dwv_presence + z_ACS_PCT_HH_PUB_ASSIST + z_AHRF_TXC_SITE_NO_CNTRL, data = Z_and_Final_Variables_10.28.22) 
summary(z_owned_levels_12345678)
```

## Final Housing Model, Owned HH
## Confidence Intervals

```{r}
confint(z_owned_levels_12345678)
```

## Final Housing Model, Owned HH
## VIF

```{r}
vif(z_owned_levels_12345678)
```